\documentclass[pdftex,letterpaper,11pt]{article}%
\usepackage[export]{adjustbox}
\usepackage{multirow}
\usepackage[arabicsections]{dpugatex}
%\usepackage{dpppl}
%\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{longtable}


\usepackage{tikz}

\usepackage[british]{babel}
\usepackage{amssymb,amsmath,warpcol,url,ctable,multirow,caption,threeparttable,float,soul,gensymb}
%\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother


\usepackage{subcaption}


\usepackage{xcolor,colortbl}%Per colorejar cel·les de les taules
\definecolor{verylightgray}{gray}{0.90}
\newcommand{\verylightgray}[1]{\cellcolor{verylightgray}#1}


\usepackage{arydshln} %Per dashed lines
\setlength\dashlinedash{1.5pt}
\setlength\dashlinegap{2.5pt}
\setlength\arrayrulewidth{0.8pt}

\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\usepackage{soul}
\setstcolor{red} % Tatxat vermell pel text a eliminar!!!!
\definecolor{lightgreen}{rgb}{0.564706,0.933333,0.564706}
\newcommand{\miquel}[1]{{\sethlcolor{lightgreen} \hl{#1}} } % To highlight with light green Miquel's comments.
\soulregister\citet7 % These \soulregister commands allow us to avoid problems between soul functions (\hl, \st, ...) and these other functions (\citet,\citep,\ref,\footnote, ...). Include more if it is necessary.
\soulregister\citep7
\soulregister\cite7
\soulregister\ref7
\soulregister\footnote7
\soulregister\textit7
\soulregister\textbf7
\soulregister\textsc7
\soulregister\`7 % for open accents.
\soulregister\'7 % for closed accents.
\soulregister\% 7 % for \%age symbol
\usepackage{tabularx,tabulary}
\usepackage[osf]{mathpazo} % Amb aquest paquet faig ús de la lletra Palatino, la que fan servir Puga, Duranton et al. Amb l'opció [osf] la numeració és "old fashion", però és incompatible amb un títol en negreta i small caps (desapareixen les small caps!). Per tant, per ara opto per NO aplicar aquesta opció.
\usepackage[abs]{overpic}

\usepackage{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks=true, breaklinks=true, citecolor= darkblue, linkcolor=blue, urlcolor=blue}

\usepackage{chngcntr}

\newcommand{\mc}[3]{\multicolumn{#1}{#2}{#3}}
\newcommand{\mcc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mcb}[1]{\multicolumn{1}{c}{\bf #1}}

\newcommand{\mr}[3]{\multirow{#1}{#2}{#3}} % Per fer Files múltiples (seguint el punt de vista de les columnes múltiples.
\newcommand{\mg}[3]{\multicolumn{#1}{#2}{\verylightgray #3}} %Combino el color de les cel·les amb al command de les columnes múltiples.



%\hypersetup{%
 % pdftitle={Race and neighborhoods in the 21$^{\text{st}}$ century},%
 % pdfauthor={Jorge De la Roca (NYU) , Ingrid Gould Ellen (NYU) and Katherine O'Regan (NYU)},%
 % pdfkeywords={race segregation, discrimination}}
%\pdfOpenFitWidth
%\pdfShowBookmarks

\onehalfspacing%
%\doublespacing%

\newenvironment{tablenote}[1]{\begin{list}{}{\vskip-5mm\relax
\setlength{\leftmargin}{#1} \setlength{\rightmargin}{\leftmargin}}
\item[]\footnotesize\vskip-7pt
{\em Notes}:\space\ignorespaces}{\end{list}}

\newcommand{\jdlradded}[1]{#1}
\newcommand{\dpadded}[1]{#1}
\newcommand{\jdlrdeleted}[1]{}
\newcommand{\dpdeleted}[1]{}
\newcommand{\jdlrcomment}[1]{}
\newcommand{\dpcomment}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\martin}[1]{{\color{blue} Martin: [{#1}]}}
\newcommand{\dani}[1]{{\color{purple} Dani: [{#1}]}}

\begin{document}
\begin{titlepage}
\vspace*{1ex}
\begin{minipage}{\textwidth}
\begin{center}%

    {\textsb{\LARGE \textit{``Decoding (urban) form and function using spatially explicit deep learning''}}}\\[4ex]%

% {\Large\textsb{Martin Fleischmann}\footnote[1]{THANKS.}\footnote[2]{Geographic
% Data Science Lab, Department of Geography and Planning, University of
% Liverpool, Roxby Building , 74 Bedford St S , Liverpool , L69 7ZT, United
% Kingdom}\footnote[4]{
% E-mail: \url{M.Fleischmann@liverpool.ac.uk}; website: \url{https://martinfleischmann.net/}.}}\\[1mm]
% %
% {\Large\textbf{Daniel Arribas-Bel}\footnotemark[1]\footnotemark[2]\footnote[3]{E-mail: \url{D.Arribas-Bel@liverpool.ac.uk}; phone: +44 (0)151 795 9727; website: \url{http://darribas.org}.
% }}\footnote[5]{The Alan Turing Institute, British Library, 96 Euston Road, London, England, NW1 2DB, United Kingdom}
% \\[1mm]
% {\large\textit{Geographic Data Science Lab, University of Liverpool} }\\
% {\large\textit{The Alan Turing Institute} }\\[2.5ex]
%
\date{\today}\vspace{1.5ex}
%
\end{center}
%
\begin{abstract}
    This paper advances our understanding of the extent to which conventional deep
    learning methods can be applied to satellite imagery to capture the composition of
    urbanised landscapes. The building blocks that make up those -the activities and
    agents conceptualised as urban function and the structure that supports them
    conceptualised as urban form- can be arranged in many ways. This paper relies on the
    concept of “spatial signatures”, a characterisation of space dependent on data
    released at a variable rate - an issue that could be resolved by remote sensing and
    satellite imagery. Using Sentinel-2 imagery, we explore this pathway within
    convolutional neural networks and predictive modelling trained to identify spatial
    signatures across Great Britain. While deep learning is established, its application
    has often ignored the geographical nature of the images. Our focus is to develop a
    performant model but also to learn about the effect of spatially explicit methods of
    doing so. The results indicate that classification of urban environments is more
    challenging than non-urban. However, when applying spatially explicit methods the
    accuracy is competitive with established models. This suggests that satellite
    imagery reflect form and function in greater detail than is usually present in
    available remote sensing products.
\end{abstract}
%
\vspace{1.5ex}
%
Key words: \hskip.25em spatial signatures, classification, remote sensing, artificial intelligence, open data\\
%
\vspace*{-1.5ex}
%
\end{minipage}
\end{titlepage}

% Section 1 - Intro
\input{s1_intro.tex}

% 1500 words

% Section 2 - Materials & Methods
\input{s2_materials_methods.tex}

% 3000 words

% Section 3 - Results
\input{s3_results.tex}

% 500 words

% Section 4 - Discussion
\input{s4_discussion.tex}

% 1000 words

\section*{Data and code availability statement}

All the data and code will be available on a public repository with DOI upon acceptance
of the article to ensure anonymity of a double-blind review.

\clearpage

\bibliographystyle{apalike}
\bibliography{refs}

\clearpage

\input{sa_appendix.tex}

\clearpage

\end{document}
